Predicting the Capture Rate of Pokemon

### 2022-11-15 Final_Draft.Rmd
progress

```{r, message = FALSE}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
library(kknn)

@@

## Loading and Exploring the Raw Data

@@

>>>>

```{r, message = FALSE}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
library(kknn)
library(dplyr)

@@

## Loading, Exploring, and Cleaning the Raw Data

@@

From the data, each of the variables that specify each Pokemon's skill against a certain type of Pokemon (i.e. `against_bug`, `against_dark`, etc.) do not appear to be as relevant as other attributes in deciding whether specifc features about a Pokemon affect its capture rate. We can also assume that the `attack` variable gives us an overall estimate of each Pokemon's attack skill so we would not need to go into such great detail as finding out how the Pokemon perform against every other type of Pokemon. For that reason, these 18 columns can be dropped.

At first, it seems that the `classification` variable may be helpful; however, let us see how many unique classifications of a Pokemon there are.

```{r}
pokemon %>%
  distinct(classfication) %>%
  count()
```

There are 588 unique classifications! That seems a little too high for our analysis so we will just stick to using the `type` of the Pokemon instead.

Furthermore, for the `abilities` variable, we can see that there is no set amount for how many abilities a Pokemon has or a measure to figure out which abilities are more powerful than others. For these reasons, it may be best to avoid including this column into our analysis.

Some other variables must also be taken out as they do not seem as if they would reveal any more information relevant to our analysis based on substantive knowledge: `weight_kg`, `pokedex_number`, `percentage_male`, `japanese_name`, `base_happiness`, `base_egg_steps`, `experience_growth`, and `height_m`.

Now, let's filter out all those unwanted variables!!

```{r}
# Selecting only the variables we want
pokemon <- pokemon %>% 
  select(c("abilities", "attack", "base_total", "capture_rate", "defense", "hp", "name", "sp_attack", "sp_defense", "speed", "type1", "generation", "is_legendary"))
head(pokemon)
```
